Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Moved a paragraph

@@

With this information we concluded that our categorisation was incorrect. It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation we being performed to meet the needs of the API users. It was also clear that the subcategory should therefore be updative.

@@

After cross examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes. While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.

>>>>

After cross examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.

@@

With this information we concluded that our categorisation was incorrect. It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation were being performed to meet the needs of the API users. It was also clear that the subcategory should therefore be updative.

@@

While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
